\section{Publications}

\begin{enumerate}
    \item \textbf{From Control to Chaos: A Comprehensive Formal Analysis of 5G’s Access Control}\\
    Mujtahid Akon, \textbf{Md. Toufikuzzaman}, Syed Rafiul Hussain\\
    In \textit{IEEE Symposium on Security and Privacy, 2025 } \fontref{https://doi.ieeecomputersociety.org/10.1109/SP61157.2025.00141}{[URL]} \fontref{https://github.com/SyNSec-den/CoreScan}{[Code]}
    
    \item \textbf{CRISPR-DIPOFF: An Interpretable Deep Learning Approach for CRISPR Cas-9 Off-Target Prediction}\\
    \textbf{Md. Toufikuzzaman}, Md. Abul Hassan Samee, M Sohel Rahman\\
    In \textit{Briefings in Bioinformatics, 2024 }  \fontref{https://academic.oup.com/bib/article/25/2/bbad530/7588687}{[URL]} \fontref{https://github.com/tzpranto/CRISPR-DIPOFF}{[Code]}
    
    \item \textbf{A Deep Learning Based Semi-Supervised Network Intrusion Detection System Robust to Adversarial Attacks}\\
    Syed. Md. Mukit Rashid*, \textbf{Md. Toufikuzzaman*}, Md. Shohrab Hossain\\
    \{*Equal contribution\}\\
    In \textit{10th International Conference on Networking, Systems and Security (NSysS), 2023}.
    \fontref{https://dl.acm.org/doi/10.1145/3629188.3629189}{[URL]}\fontref{https://github.com/tzpranto/NIDS_NSYSS_23}{[Code]}
    
    \item \textbf{Phylogenetic Analyses of SARS-CoV-2 Strains Reveal Its Link to the Spread of COVID-19 Across the Globe}\\
    Shashata Sawmya, Arpita Saha, Sadia Tasnim, Naser Anjum, \textbf{Md. Toufikuzzaman}, Ali Haisam Muhamad Rafid, Mohammad Saifur Rahman, M Sohel Rahman, Tanvir Alam\\
    In \textit{MEDINFO 2021: One World, One Health–Global Partnership for Digital Innovation}. \fontref{https://ebooks.iospress.nl/doi/10.3233/SHTI220174}{[URL]} \fontref{https://github.com/pythonLoader/Analyzing-hCov-Genome-Sequence}{[Code]}

    \item \textbf{Fault Occurrence Detection and Classification of Fault Type in Electrical Power Transmission Line with Machine Learning Algorithms.}\\
    Shameem Hasan, \textbf{Md. Toufikuzzaman}\\
    In \textit{International Journal on Electrical Engineering \& Informatics 14, 3 (2022)}. \fontref{https://www.proquest.com/openview/4147ac033610f2e5150845b519eb448d/1?pq-origsite=gscholar&cbl=316223}{[URL]} 
    
    \item \textbf{CRISPRpred (SEQ): a sequence-based method for sgRNA on target activity prediction using traditional machine learning}\\
    Ali Haisam Muhammad Rafid*, \textbf{Md. Toufikuzzaman*}, Mohammad Saifur Rahman, M Sohel Rahman\\
    \{*Equal contribution\}\\
    In \textit{BMC bioinformatics 21, 223 (2020)}. \fontref{https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-020-3531-9}{[URL]} \fontref{https://github.com/Rafid013/CRISPRpredSEQ}{[Code]}
\end{enumerate}

% \noindent Under Review/Pre-print:
% \begin{enumerate}
%     \item \textbf{CRISPR-DIPOFF: An Interpretable Deep Learning Approach for CRISPR Cas-9 Off-Target Prediction}\\
%     \textbf{Md. Toufikuzzaman}, Md. Abul Hassan Samee, M Sohel Rahman\\
%     In \textit{bioRxiv Pre-print, 2023}. \fontref{https://www.biorxiv.org/content/10.1101/2023.08.05.552139v1.full.pdf}{[PDF]} \fontref{https://github.com/tzpranto/CRISPR-DIPOFF}{[Code]}
    
% \end{enumerate}

\endinput