\section{Research Experience (Selected)} 

\begin{enumerate}
    \item \textbf{LLM Overrefusal}: In this research, I am analyzing the overrefusal behavior in Large Language Model particularly in models with Mixture of Experts. I am utilizing mechanistic interpretability to identify the experts associated with model safety and formulating techniques to address overrefusal without expensive fine-tuning process.\\
    Supervisor: \textit{Prof. Dongwon Lee and Prof. Kyusun Choi} \hfill Status: Ongoing.

    % \item \textbf{Verifiable Sustainability}: In this research, we have proposed a verifiable power metric architecture to ensure accurate and verifiable power consumption report in the cloud environment. Our proposed solution utilizes Trusted Execution Environment (TEE) and Trusted Platform Module (TPM) as trust anchor and builds the system using components like IMA, eBPF and CFI. We have already developed a working prototype and currently expanding its capability.\\
    % Supervisor: \textit{Dr. Syed Rafiul Hussin} \hfill Status: Ongoing.

    \item \textbf{5G Access Control Formal Analysis}: In this research, we presented CoreScan, a comprehensive formal analysis framework for verifying the access control mechanism of 5G core networks, including indirect communication and roaming. Leveraging assume-guarantee reasoning and compositional verification, CoreScan systematically uncovered five new classes of exploitable privilege escalation vulnerabilities and confirmed that prior over-privilege flaws extend to more complex 5G scenarios. The findings were responsibly disclosed to GSMA and led to proposed updates in 5G security specifications.\\
    Supervisor: \textit{Dr. Syed Rafiul Hussain} \hfill Status: Published in IEEE S\&P 2025.

    
    \item \textbf{Flood Detection}: This is a multidisciplinary research focusing on the application of machine learning to design an end-to-end early flood detection system using satellite images. One of the core challenges of satellite images is that the presence of clouds makes the signals from the visible band unusable. One of the main indicators for flood is the NDW-Index which is calculated from the visible band. As a part of this project, we have designed an U-net image model to directly generate NDWI from other bands in the cloudy environment. Currently this work is under review for publication.\\
    Supervisor: \textit{Dr. M. Sohel Rahman} \hfill Status: Under Review.
    
    \item \textbf{CRISPR-DIPOFF}: In this research, we have thoroughly explored deep learning networks, particularly the recurrent neural network (RNN) and transformer-based models, leveraging their established success in handling sequence data. Furthermore, we have employed evolutionary algorithms for hyperparameter tuning to optimize these models’ performance and interpreted the models using integrated gradients. We not only outperformed the existing state-of-the-art models but also identified the presence of two sub-regions in the seed region of sgRNA which extends the established biological hypothesis of Off-Target effects.\\
    Supervisor: \textit{Dr. M. Sohel Rahman} \hfill Status: Published in \textit{BiB, 2023}.

    % \item \textbf{CRISPR-DIPOFF}: In this research, we have thoroughly explored deep learning networks, particularly the recurrent neural network (RNN) and transformer-based models, leveraging their established success in handling sequence data. Furthermore, we have employed genetic algorithm for hyperparameter tuning to optimize these models’ performance. The results from our experiments demonstrate significant performance improvement compared to the current state-of-the-art in Off-Target prediction, highlighting the efficacy of our approach. Furthermore, leveraging the power of the integrated gradient method, we have made an effort to interpret our models resulting in a detailed analysis and understanding of the underlying factors that contribute to Off-Target predictions, in particular the presence of two sub-regions in the seed region of sgRNA which extends the established biological hypothesis of Off-Target effects.\\
    % Supervisor: \textit{Prof. M. Sohel Rahman} \hfill Status: Conditionally accepted in \textit{BiB, 2023}.
    
    % \item \textbf{NIDS}: In this research, we presented a novel semi-supervised and adversarially robust deep learning-based approach which can utilize both labeled and unlabeled training samples. Our proposed pipeline first performs K-Means clustering to soft label part of the unlabeled data and then obtain a decision tree based on labeled and soft labeled samples. It then pretrains an autoencoder based multi-layer perceptron and later learns separate multi-layer perceptrons on each individual leaf of the decision tree. Our results show that the performance of our system is comparable to state-of-the art supervised learning approaches and outperforms existing state-of-the-art semi-supervised NIDS. Furthermore, we have extensively tested the adversarial robustness of our method using the popular blackbox Fast Gradient Sign Method (FGSM) and Generative Adversarial Network based IDSGAN approaches.\\
    % Supervisor: \textit{Prof. Md. Shohrab Hossain} \hfill Status: Accepted in \textit{NSysS, 2023}.

    \item \textbf{NIDS}: In this research, we presented a novel semi-supervised and adversarially robust deep learning-based approach which can utilize both labeled and unlabeled training samples. Our model consists of a set of heterogeneous components like K-Means clustering, Autoencoder, Decision Trees, and Multi-Layer Perceptions to ensure adversarial robustness. We have extensively tested the adversarial robustness of our method using the popular blackbox Fast Gradient Sign Method (FGSM) and Generative Adversarial Network based IDSGAN approaches.\\
    Supervisor: \textit{Dr. Md. Shohrab Hossain} \hfill Status: Published in \textit{NSysS, 2023}.
    
    % \item \textbf{Analyzing hCov Genome Sequences}: In this research, we presented an analysis pipeline comprising a classification exercise to identify the virulence of the genome sequences and extraction of important features from its genetic material that are used subsequently to predict mutation at those interesting sites using deep learning techniques.\\
    % Supervisor: \textit{Prof. M. Sohel Rahman} \hfill Status: Published in \textit{MEDINFO, 2021}.
    
    % \item \textbf{CRISPRPred(SEQ)}: In this research, we presented CRISPRpred(SEQ), a method for sgRNA on-target activity prediction that leverages only traditional machine learning techniques and hand-crafted features extracted from sgRNA sequences. The inclusion of K-mer and n-Gapped nucleotide-based features proved to be defining factors in CRISPR On-target prediction and outperformed even the existing deep learning models.\\
    % Supervisor: \textit{Dr. M. Sohel Rahman} \hfill Status: Published in \textit{BMC Bioinformatics, 2020}.    
\end{enumerate}

\endinput